\section{User Stories}

\subsection{Prioritized User Stories}

\noindent
1. As a frequent traveler, I want to subscribe to a comprehensive monthly pass that includes all three networks so that I can save money on my regular commutes. \textbf{QAs:} Usability

\noindent
2. As a passenger, I want to be able to check the balance of my multi-network travel card online so that I can easily manage my travel expenses. \textbf{QAs:} Usability

\noindent
13. As a family, we want to charge train cards from the terminal, so that we can travel when we need without one transaction every time. \textbf{QAs:} Usability(+), Modifiability(-)

\noindent
15. As an occasional passenger, I want the system to not allow me to pay for temporarily blocked routes, so that I don't have to go through customer service. \textbf{QAs:} Usability(+), Modifiability(-), Performance(-)

\noindent
16. As a passenger, I want to be able to purchase a single ticket that allows me to travel across all train networks so that I can travel seamlessly without needing to buy separate tickets for each tycoon's network. \textbf{QAs:} Usability(+), Modifiability(-), Performance(-)

\noindent
18. As a government regulator, I want the payment system to adhere to data protection and financial transaction security standards so that passengers' personal and financial information is secure. \textbf{QAs:} Security(+), Modifiability(-), Testability(-), Integrability(-)

\noindent
23. As a tycoon, I want the payment system to integrate with my existing infrastructure with minimal disruption so that I can maintain high service levels during the transition. \textbf{QAs:} Integrability(+), Modifiability(-), Usability(+), Testability(-)

\noindent
26. As a station manager, I want the system to offer real-time updates on train schedules and network disruptions so that I can keep passengers informed and manage station flow effectively. \textbf{QAs:} Usability(+), Performance(-)

\noindent
27. As a network maintenance planner, I want the payment system to integrate with maintenance scheduling tools so that I can plan work with minimal disruption to the train service and revenue. \textbf{QAs:} Availability(+), Modifiability(-)

\subsection{Passengers}

\noindent
1. As a frequent traveler, I want to subscribe to a comprehensive monthly pass that includes all three networks so that I can save money on my regular commutes. \textbf{QAs:} Usability

\noindent
2. As a passenger, I want to be able to check the balance of my multi-network travel card online so that I can easily manage my travel expenses. \textbf{QAs:} Usability

\noindent
3. As a passenger with a subscription, I want to receive automatic notifications about my subscription renewal and any discounts or promotions available so that I can take advantage of cost savings. \textbf{QAs:} Usability

\subsection{Tech-savvy Passengers}

\noindent
4. As a tech-savvy passenger, I want to use a mobile app to manage my subscriptions, make payments, and receive digital tickets so that I can have a paperless and convenient travel experience. \textbf{QAs:} Usability(+), Deployability(-)

\noindent
5. As a passenger interested in sustainability, I want the system to track my travel carbon footprint and offer carbon offset options so that I can make environmentally responsible travel choices. \textbf{QAs:} Energy efficiency(+), Performance(-)

\subsection{Accessibility Advocates}

\noindent
6. As a passenger with mobility challenges, I want the payment system to provide information on accessible services and allow for easy purchase of accessible seating across all networks so that I can travel comfortably and safely. \textbf{QAs:} Usability(+), Safety(+)

\noindent
7. As an advocate for accessibility, I want the system to offer voice-activated features and screen reader compatibility for passengers with visual impairments so that the service is inclusive and accessible to everyone. \textbf{QAs:} Usability(+), Modifiability(-), Deployability(-)

\noindent
8. As an elder, I want a simple interface, so that I don't have to get help to buy tickets. \textbf{QAs:} Usability(+), Modifiability(+)

\noindent
9. As a tourist, I want to choose among many languages, so that I don't have to translate using my phone. \textbf{QAs:} Usability(+), Modifiability(-)

\noindent
10. As a tourist, I want to have quick access to the most popular trips, so I can quickly get my ticket. \textbf{QAs:} Usability(+), Modifiability(-), Performance(-)

\noindent
11. As a student, I want to be able to scan my student card, so that I can access financial benefits. \textbf{QAs:} Usability(+), Modifiability(-)

\noindent
12. As a commuting worker / student, I want a single transaction to get all the subscriptions I need, so that I can travel from home to work every day. \textbf{QAs:} Usability(+), Performance(-)

\noindent
13. As a family, we want to charge train cards from the terminal, so that we can travel when we need without one transaction every time. \textbf{QAs:} Usability(+), Modifiability(-)

\noindent
14. As a visually impaired person, I want a high contrast interface and big font, so that I can avoid mistakes when buying my tickets. \textbf{QAs:} Usability(+)

\noindent
15. As an occasional passenger, I want the system to not allow me to pay for temporarily blocked routes, so that I don't have to go through customer service. \textbf{QAs:} Usability(+), Modifiability(-), Performance(-)

\noindent
16. As a passenger, I want to be able to purchase a single ticket that allows me to travel across all train networks so that I can travel seamlessly without needing to buy separate tickets for each tycoon's network. \textbf{QAs:} Usability(+), Modifiability(-), Performance(-)

\noindent
17. As a student/commuter, I want the system to tell me which subscriptions I need to go from home to school/work, so that I can get the best price. \textbf{QAs:} Usability(+), Performance(-), Modifiability(-)

\subsection{Government}

\noindent
18. As a government regulator, I want the payment system to adhere to data protection and financial transaction security standards so that passengers' personal and financial information is secure. \textbf{QAs:} Security(+), Modifiability(-), Testability(-), Integrability(-)

\noindent
19. As a government entity, I want the system to provide detailed reporting on passenger numbers and revenue for each network so that we can assess the public transportation system's efficiency and fairness. \textbf{QAs:} Usability(+), Modifiability(-), Integrability(-)

\noindent
20. As a local government official, I want to ensure that the payment system includes options for reduced fares for eligible populations (students, elderly, low-income) across all networks so that public transportation is accessible to everyone. Also, as a local government, I want to get usage data from the system, so that I can do urban planning properly. \textbf{QAs:} Usability(+), Performance(-), Modifiability(-)

\subsection{Tycoons (Train Company Owners)}

\noindent
21. As a tycoon, I want the payment system to accurately track revenue from shared and exclusive segments of my network so that revenue sharing among tycoons is fair and transparent. \textbf{QAs:} Usability(+), Performance(-), Modifiability(-)

\noindent
22. As a tycoon, I want the ability to offer exclusive promotions and discounts to passengers using my network to encourage loyalty and increase ridership. \textbf{QAs:} Usability(+), Modifiability(-)

\noindent
23. As a tycoon, I want the payment system to integrate with my existing infrastructure with minimal disruption so that I can maintain high service levels during the transition. \textbf{QAs:} Integrability(+), Modifiability(-), Usability(+), Testability(-)

\noindent
24. As a tycoon, I want to access analytics and data insights from the payment system to understand passenger behavior and adjust my services accordingly to maximize revenue and improve service. \textbf{QAs:} Integrability(+), Modifiability(-)

\subsection{Financial Analysts}

\noindent
As a financial analyst for a tycoon, I want the system to provide detailed financial analytics and forecasting tools so that we can optimize pricing strategies and revenue across the shared network. \textbf{QAs:} Availability(+), Modifiability(-)

\subsection{Station Staff}

\noindent
25. As a station staff member, I want a simple and fast way to assist passengers with ticket purchases and inquiries across all networks so that I can provide efficient customer service. \textbf{QAs:} Usability(+), Modifiability(-)

\subsection{Maintenance Teams}

\noindent
26. As a maintenance team member, I want the system to allow for temporary fare adjustments or bypass options during maintenance work so that we can minimize inconvenience to passengers. \textbf{QAs:} Availability(+), Modifiability(-)

\noindent
27. As a network maintenance planner, I want the payment system to integrate with maintenance scheduling tools so that I can plan work with minimal disruption to the train service and revenue. \textbf{QAs:} Availability(+), Modifiability(-)

\subsection{Government Financial Auditors}

\noindent
28. As a government financial auditor, I want the payment system to include audit trails and compliance reporting features so that we can ensure transparency and accountability in revenue management.

\subsection{TRiP Owner}
\noindent
28. As the TRiP owner, I want to use a service-based architecture, so that the system is easy to maintain and update.

\noindent
29. As the TRiP owner, I want the system to operate with the lowest possible operational costs, so that it remains cost-effective over time.

\noindent
30. As the TRiP owner, I want the system maintenance efforts to be easily scalable, so that costs do not increase disproportionately as we expand.

\noindent
31. As the TRiP owner, I want routine maintenance tasks to be automated, so that manual labor and operational costs are reduced.

\noindent
32. As the TRiP owner, I want a cost-effective database solution for data management, so that storage and access costs remain low.

\noindent
33. As the TRiP owner, I want an efficient error handling and reporting mechanism, so that system downtime is minimized and maintenance is cost-effective.

\noindent
34. As the TRiP owner, I want to implement energy-efficient and eco-friendly technologies, so that the system's operational costs are sustainable and environmentally friendly.

\end{document}
