\section*{Decision 4: How to integrate subscription to route optimization module}

\subsection*{Status}
Review

\subsection*{Architectural Summary}
In developing the TrIP system, we explore subscription model architectures that align railway tycoons' need for flexibility with passengers' demand for simplicity. 
We assess the trade-offs between unified and tycoon-specific models to enhance both operational autonomy and passenger convenience.

\subsection*{Concern}
A user wants to know the available tickets from A-B. 
Connected user stories: 16 (passenger want one payment for many trains), 23 (tycoon wants easy integration with their system)

\subsection*{Context}
When passengers want to go from station A to station B, they want to be able to use all the subscription they have and pay for the trains belonging to tycoons they are not subsribed to.
The terminal has to communicate with the tycoon systems to verify subscriptions and check routes.

\subsection*{Criteria}
\begin{itemize}
\item Ease of use for the passenger.
\item Multiple route options for the user.
\item The system returns to user usable options based on price/time/availability/subscription.
\item Simple integration with the tycoon systems.
\end{itemize}

\subsection*{Option 1: Introduction of a subscription manager tool, route optimizer needs to take subs into consideration.}
We want to include a Subscription Manager module to our functional view. 
Such a module has the responsibility to verify subscriptions, communicating with the tycoon system.
Furthermore, the Route Optimizer module needs to be able to optimize wrt price given that the passenger holds some subscription.
The idea is to add an optional initial iteration to the sequence of actions sketched in decision3.
This requires a way to communicate the subscription to the terminal, be it a QR code, a code or a magnetic card. 
This should be the topic of another decision.

The functional view schema is in my bag.

\subsection*{Option 2: }


\subsection*{Decision}

\subsection*{Consequences}
\textbf{Positive Consequences:}
\begin{itemize}
\end{itemize}
\textbf{Negative Consequences:}
\begin{itemize}
\end{itemize}