\subsection{Decision 14: Handling Network Outages}

\subsection*{Status}
Open

\subsection*{Architectural Summary}
\begin{tabular}{|p{3.5cm}|p{10.5cm}|}
    \hline
    \textbf{In the context of} & Ensuring uninterrupted service and data integrity during network outages in the TRiP system. \\
    \hline
    \textbf{Facing} & The challenge of maintaining operational continuity and securing transactions in the absence of network connectivity. \\
    \hline
    \textbf{To achieve} & A resilient system capable of handling ticket validations and transactions securely, even during network disruptions. \\
    \hline
    \textbf{We considered} & Option 1: Delayed Processing; Option 2: Local Caching, \\
    \hline
    \textbf{And decided for} & A hybrid approach utilizing delayed processing and strategic local caching for essential operations. \\
    \hline
    \textbf{Because} & This method balances the need for operational continuity with security and data integrity, catering to the immediate needs of users while addressing potential security risks. \\
    \hline
    \textbf{Accepting} & The complexity of managing dual mechanisms and potential security concerns related to local data storage. \\
    \hline
\end{tabular}

\subsection*{Concern}
Ensuring system resilience and continuous operation during network disruptions.
Related user stories are listed here:
\begin{itemize}
    \item \textbf{User Story 39:} As a passenger, I expect ticket validation to work seamlessly, even during network outages, ensuring that my travel is not hindered by technical issues.
    \item \textbf{User Story 40:} As a tycoon, I require the system to handle all transactions securely and efficiently, irrespective of the current network status, to maintain service continuity and safeguard revenue. 
\end{itemize}

\subsection*{Context}
Network outages pose significant challenges to real-time processing capabilities, affecting ticket validations and financial transactions.

\subsection*{Criteria}
\begin{itemize}
    \item \textit{Availability}: Minimize service disruption during network outages.
    \item Ensure data \textit{security} and integrity, especially for financial transactions.
    \item \textit{Performance}: Optimize local data storage to balance operational continuity with security risks.
\end{itemize}

\subsection*{Option 1: Delayed Processing}
Transactions are processed once network connectivity is restored, minimizing the need for local data storage but risking transaction backlog.

\subsection*{Option 2: Local Caching}
Local caching of critical data to enable processing during outages, with careful consideration of security implications due to increased local data storage.

\subsection*{Decision}
A combination of Option 1 and strategic caching for essential data will be used for delayed processing. This approach is chosen to maintain service reliability while addressing security concerns.
This decision balances the need for uninterrupted service during network outages against the risks associated with local data storage. It considers the priority of user experience and security as per stakeholder requirements and aligns with previous decisions to enhance system resilience.

\subsection*{Consequences}
\textbf{Positive Consequences:}
\begin{itemize}
    \item Maintains ticket validation and system operations during network outages, enhancing user experience.
    \item Reduces the risk of service disruption, aligning with the expectations of users and tycoons.
    \item Balances operational needs with security concerns through selective data caching.
\end{itemize}
\textbf{Negative Consequences:}
\begin{itemize}
    \item May introduce a risk of negative balances due to delayed processing of financial transactions.
    \item Increases system complexity with the need to manage both delayed processing and data caching mechanisms.
    \item Poses potential security risks related to the local storage of sensitive data, despite limited caching.
\end{itemize}
